A numerical study of the solution of X-Mode equations around the hybrid resonance

### 2015-04-23 report_clean/responce_reviewers.tex

\maketitle

\begin{abstract}

\end{abstract}

\section{Extra Corrections}
As an extra improvement, not asked by the reviewers, we changed $\tilde{\omega}$ to $\omega_{\nu}$ in Section 2.

Corrected the definitions of $\alpha,\delta$ to comply with the definition of the cold plasma dielectric tensor of Stix (more precisely, removed terms $\frac{\omega^2}{c^2}$ in 
front of them)

@@

\section{Responce to the reviewer #1}

All the corrections are marked in blue.

A. General issues.

1. We agree with the remarks of the reviewer. We included a short introduction into the physics of the problem, 
which hopefully will facilitate in reading the article. The Section 4.3.1 contains of course a mistake in the description of the 
parameters of the problem.

Concerning the notation: from now on $\epsilon^{\nu}_{\omega}(\mathbf{r})$ denotes the cold plasma dielectric tensor, similarly we denote its parameters.

 We added explicitely dependence on space in parameters 
that depend on the spatial variables.

- as mentionned above, in Lemma 2.1 it would be clearer to write "\omega \neq \omega_c" than "\hat \epsilon < + \infty"
(especially given that \hat \epsilon is not defined in Lemma 2.1).

We added as well a brief description of what limiting absorption and limiting amplitude principles

### 2015-04-23 report_clean/FD.tex
Afterwards say that from now on we define $epsilon_0(x)=epsilon(x)$
bug fix"
changed notation, corrected some defs

\section{Frequency domain study}
In the frequency domain, the velocity can be eliminated and it yields a simpler system under the form
of  Maxwell equations with the cold plasma dielectric tensor \cite{Stix,Despres_2014}. One obtains the equations
\bealn
%\label{eq:main_frequency_domain_1}
\operatorname{curl}\operatorname{curl}\hat{\mathbf{E}}-
\epsilon(\omega)\hat{\mathbf{E}}=0,\\
\epsilon(\omega)=\left(
\begin{matrix}
 \tilde{\alpha} & i\tilde{\delta} \\
 -i\tilde{\delta}  & \tilde{\alpha}
\end{matrix}
\right),\\
\tilde{\alpha}(\omega,x)=\frac{\omega^2}{c^2}\left(1-\frac{\tilde{\omega}\omega_p^2}{\omega(\tilde{\omega}^2-\omega_c^2)}\right),\qquad 
\tilde{\delta}(\omega)=\frac{\omega_c\omega_p^2}{\omega(\tilde{\omega}^2-\omega_c^2)},
\eealn
where the frequency 
$\tilde{\omega}=\omega+i\nu$ is shifted in the complex plane,
the cyclotron frequency is 
$ \omega_c={\frac{eB_0}{m_e}}$ and the plasma frequency is $ \omega_p^2=\frac{e^2 N_e}{\epsilon_0 m_e}$.
The series expansion as $\nu\rightarrow 0$ gives at leading orders
\bealn
 \tilde{\alpha}(\omega,x)=\alpha(\omega,x)+i\nu\frac{\omega_p^2(\omega^2+\omega_c^2)}{(\omega^2-\omega_c^2)^2}\frac{\omega^2}{c^2},\qquad \alpha(\omega)=\frac{\omega^2}{c^2}\left(1-\frac{\omega_p^2}{\omega^2-\omega_c^2}\right),\\
 \tilde{\delta}(\omega)=\delta(\omega)-\frac{2i\omega^3\nu}{c^2(\omega^2-\omega_c^2)^2},\qquad \delta(\omega)=\frac{\omega\omega_c\omega_p^2}{c^2(\omega^2-\omega_c^2)}.
\eealn
We finally obtain a simpler equation \cite{Despres_2014} 
%\ben
% \epsilon_{\nu}(\omega)\approx \epsilon_0+i\nu Id,\; \nu\rightarrow 0.
%\een
%Thus, in this work we concentrate on a model
\begin{align}
\label{eq:main_frequency_domain}
\operatorname{curl}\operatorname{curl}\hat{\mathbf{E}}-\frac{\omega^2}{c^2}
\left(\epsilon_0(\omega)+\nu Id\right)\hat{\mathbf{E}}=0,\\
\label{eq:epsilon_0}
\epsilon_0(\omega)=\left(
\begin{matrix}
 \alpha & i\delta \\
 -i\delta & \alpha 
\end{matrix}
\right).
\end{align}
 In this model problem, the coefficients  $\alpha(\omega,x)$ and $\delta(\omega)$ are sufficiently smooth, i.e. bounded and continuous in  
$\left[-L,\; \mathbb{R}\right)$.

>>>>

\section{Frequency domain study}
The goal of this section is to review the connection between the system (\ref{eq:main_system}), its frequency domain counterpart and 
the regularized problem (\ref{eq:seq_regularized}).

In the frequency domain, the velocity can be eliminated to obtain a simpler system under the form
of  Maxwell equations with the cold plasma dielectric tensor \cite{Stix,Despres_2014}, more precisely
\urev{
\bealn
%\label{eq:main_frequency_domain_1}
\operatorname{curl}\operatorname{curl}\hat{\mathbf{E}}-
\frac{\omega^2}{c^2}\underline{\epsilon}^{\nu}_{\omega}(\mathbf{r})\hat{\mathbf{E}}=0,\\
\underline{\epsilon}^{\nu}_{\omega}(\mathbf{r})=\left(
\begin{matrix}
 \alpha^{\nu}_{\omega}(\mathbf{r}) & i\delta^{\nu}_{\omega}(\mathbf{r}) \\
 -i\delta^{\nu}_{\omega}(\mathbf{r}) & \alpha^{\nu}_{\omega}(\mathbf{r})
\end{matrix}
\right),\qquad 
 \alpha^{\nu}_{\omega}(\mathbf{r})=\frac{\omega^2}{c^2}\left(1-\frac{\omega_{\nu}\omega_p^2(\mathbf{r})}{\omega(\omega_{\nu}^2-\omega_c^2(\mathbf{r}))}\right),\qquad 
\delta^{\nu}_{\omega}(\mathbf{r})=\frac{\omega_c(\mathbf{r})\omega_p^2(\mathbf{r})}{\omega(\omega_{\nu}^2-\omega_c^2(\mathbf{r}))},
\eealn
}
\mrev{where the frequency 
$\omega_{\nu}=\omega+i\nu$ is shifted in the complex plane. Note that neither cyclotron, nor hybrid resonances occur in the problem with the dielectric tensor $\epsilon^{\nu}_{\omega}(\mathbf{r}), \; \nu>0,$ (since all parameters are real). Hence 
the choice of the non-zero plasma friction $\nu>0$ can be viewed as a regularization of the problem. }

\mrev{
The series expansion as $\nu\rightarrow 0$ gives at leading orders
\bealn
 \alpha^{\nu}_{\omega}=\alpha^{0}_{\omega}+i\nu\frac{\omega_p^2(\omega^2+\omega_c^2)}{(\omega^2-\omega_c^2)^2}=\alpha^{0}_{\omega}+i\nu D_{\alpha},\\
 \delta^{\nu}_{\omega}=\delta^{0}_{\omega}-i\nu\frac{2\omega}{(\omega^2-\omega_c^2)^2}=\alpha^{0}_{\omega}+i\nu D_{\delta},
\eealn
where $\alpha^{0}_{\omega},\;\delta^{0}_{\omega}$ are defined by (\ref{eq:alpha_delta}). In the frequency domain one thus can consider 
the following regularization of the cold plasma dielectric tensor of (\ref{eq:main_frequency_domain}):
\begin{align*}
\underline{\epsilon}^{\nu}_{\omega}\approx \underline{\epsilon}^0_{\omega}+i\nu \left(
 \begin{matrix}
  D_{\alpha} & D_{\delta}\\
  -D_{\delta} & D_{\alpha}
 \end{matrix}
\right).
\end{align*}
However, as demonstrated in \cite{singular_solutions} for the 1D setting, a significantly simpler regularization (considered in \cite{Despres_2014})
\ben
\epsilon^{\nu}_{\omega}(\mathbf{r})\approx \epsilon^{0}_{\omega}(\mathbf{r})+i\nu \mathbb{E}
\een
yields the same solution as $\nu\rightarrow 0$. }
%We finally obtain a simpler equation \cite{Despres_2014}

\textcolor{red}{Thus, applying the above process to (\ref{eq:main_model}), we obtain, see also \cite{Despres_2014},
\begin{align}
\label{eq:main_frequency_domain}
\left(
\begin{matrix}
 i\theta \partial_x \hat{E}_y+\theta^2 \hat{E}_x\\
 i\theta \partial_x \hat{E}_x -\partial_x^2 \hat{E}_y
\end{matrix}
\right)-\frac{\omega^2}{c^2}
\left(\epsilon^{0}_{\omega}(x)+\nu \mathbb{E}\right)\left(
\begin{matrix}
 \hat{E}_x\\
 \hat{E}_y
\end{matrix}
\right)
=0,\\
\label{eq:epsilon_0}
\epsilon^0_{\omega}(x)=\left(
\begin{matrix}
 \alpha_{\omega}^{0}(x) & i\delta_{\omega}^{0}(x) \\
 -i\delta_{\omega}^{0}(x) & \alpha_{\omega}^{0}(x)
\end{matrix}
\right)=
\left(
\begin{matrix}
 \alpha(x) & i\delta(x) \\
 -i\delta(x) & \alpha(x)
\end{matrix}
\right).
\end{align}
 In this model problem, the coefficients  $\alpha(x)$ and $\delta(x)$ are sufficiently smooth, i.e. bounded and continuous in  
$\left[-L,\; H\right)$.
}

### 2015-04-23 report_clean/intro.tex
changed notation, corrected some defs

To illustrate unexpected difficulties that can occur in this system, let us rewrite it in the frequency domain. To do so, 
we introduce the plasma frequency $\omega_p(\mathbf{r})=\sqrt{\frac{|e|^2N_e(\mathbf{r})}{m\epsilon_0}}$, 
the cyclotron frequency $\omega_c(\mathbf{r})=\frac{e B_0(\mathbf{r})}{m_e}$ and perform the Fourier transform 
in time of \ref{eq:main_system} ($\partial_t\rightarrow -i\omega$), for a 
particular case $\nu=0$:
\begin{align}
\label{eq:model_freq_domain}
 \mathbf{curl}{\operatorname{curl}}\hat{\mathbf{E}}-\frac{\omega^2}{c^2}\underline{\epsilon}^{0}(\omega,\mathbf{r})\hat{\mathbf{E}}=0,
\end{align}
where the cold-plasma dielectric tensor \cite[Chapter 1-2]{Stix}
\begin{align*}
\underline{\epsilon}^{0}(\omega,\mathbf{r})=\left(
 \begin{matrix}
  \alpha(\mathbf{r}) & i\delta(\mathbf{r})\\
  -i\delta(\mathbf{r}) & \alpha(\mathbf{r})
 \end{matrix}
\right),\; \alpha(\mathbf{r})=1-\frac{\omega_p^2(\mathbf{r})}{\omega^2-\omega_c^2(\mathbf{r})},\; \delta=\frac{\omega_c(\mathbf{r})\omega_p^2(\mathbf{r})}{\omega(\omega^2-\omega_c^2(\mathbf{r}))}.
\end{align*}

The point $\mathbf{r}_c=(x_c,y_c)$ s.t. $\omega_c(\mathbf{r}_c)=\omega$, i.e. when $\underline{\epsilon}(\omega,\mathbf{r})$ is singular, is called a cyclotron resonance (c.f. \cite[Chapter 1-5]{Stix}). 
In \cite{singular_solutions} it was demonstrated for a 1D-counterpart of the above system that such points behave like removable singularities, 
and the solutions are well-defined in the limit $x\rightarrow x_c$. Hence this case is not of interest for the present work.

Another interesting case is $\omega_p^2(\mathbf{r})+\omega_c^2(\mathbf{r})=\omega^2$, when the diagonal part of the tensor $\underline{\epsilon}(w,\mathbf{r})$ vanishes, 
under the condition that the non-diagonal part remains non-zero. This is a hybrid resonance case. 
As shown in \cite{Despres_2014, singular_solutions}, for a 1D-counterpart of (\ref{eq:model_freq_domain}), in this case the time-harmonic electric field component $E_x$ is not necessarily square 
integrable. This apparent paradox is of course the source of important numerical difficulties which are the subject of the present study.  
Jumping ahead, instead of (\ref{eq:model_freq_domain}) 
one considers a sequence of regularized problems
\begin{align}
\label{eq:seq_regularized}
  \mathbf{curl}{\operatorname{curl}}\hat{\mathbf{E}}-\frac{w^2}{c^2}\underline{\epsilon}^{\nu}(w,\mathbf{r})\hat{\mathbf{E}}=0,\;
  \underline{\epsilon}^{\nu}(\omega,\mathbf{r})= \underline{\epsilon}^{0}(\omega,\mathbf{r})+i\nu \mathbb{E},\; 
\end{align}
with $\nu\rightarrow 0$. 
}

\urev{In some physical applications (e.g. when modelling antennas in plasmas), it is required to study the above system in an 
infinite domain $(-L,\; \infty)\times\mathbb{R}$, $L\in \mathbb{R}$,
c.f. e.g. \cite{Despres_2014}. We complement Problem (\ref{eq:model_freq_domain}) with the boundary conditions.
At the left boundary of the domain, which represents the wall of the Tokamak, we choose Robin boundary conditions 
\be
-curl \hat{\mathbf{E}} -\imath \lambda\hat{\mathbf{E}} \wedge \n = g_{inc} = -curl \E_{inc} -\imath\lambda\E_{inc} \wedge \n,
\ee
where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$ and $\lambda$ is 
the frequency of the antenna.

Therefore, we will concentrate on a 1D-version of the system (\ref{eq:main_model}), similarly to works \cite{Despres_2014, singular_solutions}. 
It already contains difficulties intrinsic to the hybrid resonance case. We truncate the domain 
$(-L,\; \infty)$ to $(-L,\; H)$ and set on the right boundary $\operatorname{curl} \E = 0$. }

Hence, we perform the Fourier transform in $y$ ($\partial_y\rightarrow i\theta$) and consider the one-dimensional setting

\begin{equation}
\label{eq:main_model}
\begin{cases}
\epsilon_0\partial_t E_{x}=-eN_e u_x,\\
\epsilon_0\partial_t E_{y}+\partial_x H_z=-eN_e u_y,\\
\mu_0\partial_t H_z+\partial_x E_y =0,\\
m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\\
m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y
\end{cases}
\end{equation}
 posed in $(-L,\; H)$, for some $L,H>0$, with the boundary conditions 
 \begin{align*}
  \left.\left(-\partial_x E_y+i\theta E_x -\imath \lambda E_y\right)\right|_{x=-L} =g_{inc},\\
  \left.\partial_xE_y\right|_{x=H}=0.
 \end{align*}

@@

%\begin{remark}
%	When modelling antennas in plasma physics \mrev{(e.g. in such applications as ITER)}, 
%	a good choice of boundary condition could be $\lambda = \sqrt{\alpha(-L)}$
%\end{remark}

@@

Second, we briefly develop an original scheme based on widely appreciated semi-lagrangian schemes
for the discretization of time domain Maxwell's equations with a linear current.
Thirdly, we consider the case $\nu\rightarrow 0$, and study the limiting amplitude solution 
$\lim\limits_{t\rightarrow +\infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}(t)$ obtained with the help of 
the FDTD discretization of \eqref{eq:main_model}, suggested in \cite{stable_yee_plasma_current}. 
We compare this result with 
$\hat{\mathbf{E}}\mathrm{e}^{i\omega t}$, computed in the frequency domain, for $\nu\rightarrow 0$, which is equivalent to considering
$\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}\mathbf{E}(t)$.
\textcolor{red}{Such a comparison is a way to study the formal commutation relation between the limited absorption and the limiting amplitude principle. 
In application to e.g. non-resonant case of (\ref{eq:model_freq_domain}), the limited absorption principle states that with 
appropriately chosen boundary conditions the solution of (\ref{eq:seq_regularized}) 
as $\nu\rightarrow 0\pm$ 
would coincide with the solution of (\ref{eq:model_freq_domain}). Similarly, the limiting amplitude principle applied to the problem (\ref{eq:main_system}) 
states that if the boundary conditions are chosen harmonic in time, e.g. $\partial_x E_y=\mathrm{e}^{-i\omega_{*} t}$ on 
the boundary, then the solution of this problem $(\mathbf{E}(t),\;H(t))$ asymptotically ($t\rightarrow +\infty$)
tends to a steady state of the form $ \left(\mathbf{E}(\omega_{*}),\; \hat{H}(\omega_{*})\right)\mathrm{e}^{-i\omega_{*} t}$, where 
$\left(\hat{\mathbf{E}}(\omega_{*}),\; \hat{H}(\omega_{*})\right)$ is the solution of (\ref{eq:main_model})
in the frequency domain, with $\omega=\omega_{*}$. The commutation between the two principles then write as}
$$
\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}= \lim\limits_{t\rightarrow+\infty}\lim\limits_{\nu\rightarrow 0},
$$
see Figure \ref{fig:limits}. 
Even though it is true for standard linear wave problems, it is not clear \mrev{if it still holds} in our case due the singularity
of the hybrid resonance.
\begin{figure}
\begin{tikzpicture}
   \matrix (m) [matrix of math nodes,row sep=3em,column sep=4em,minimum width=2em] {
     \mathbf{E}^{\nu}(t) & \mathbf{E}^{0+}(t)\\
     \hat{\mathbf{E}}^{\nu}(t)\mathrm{e}^{i\omega t} & 
    \lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow \infty}\mathbf{E}^{\nu}(t)=\lim\limits_{t\rightarrow \infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}^{\nu}(t)\\
     };
 \path[-stealth,font=\scriptsize]    (m-1-1) edge node [left] {$t\rightarrow+\infty$} (m-2-1);
  \path[-stealth, font=\scriptsize]   (m-1-1) edge node [above] {$\nu\rightarrow 0+$} (m-1-2);
 \path[-stealth, font=\scriptsize]   (m-2-1) edge node [above] {$\nu\rightarrow 0$} (m-2-2);
  \path[-stealth, font=\scriptsize]   (m-1-2) edge node [right] {$t\rightarrow +\infty$} (m-2-2);

>>>>

To illustrate unexpected difficulties that can occur in this system, let us rewrite it in the frequency domain. To do so, 
we introduce the plasma frequency $\omega_p(\mathbf{r})=\sqrt{\frac{|e|^2N_e(\mathbf{r})}{m\epsilon_0}}$, 
the cyclotron frequency $\omega_c(\mathbf{r})=\frac{e B_0(\mathbf{r})}{m_e}$ and perform the Fourier transform 
in time of \ref{eq:main_system} ($\partial_t\rightarrow -i\omega$), for a 
particular case $\nu=0$:
\begin{align}
\label{eq:model_freq_domain}
 \mathbf{curl}{\operatorname{curl}}\hat{\mathbf{E}}-\frac{\omega^2}{c^2}\underline{\epsilon}^{0}_{\omega}(\mathbf{r})\hat{\mathbf{E}}=0,
\end{align}
where the cold-plasma dielectric tensor \cite[Chapter 1-2]{Stix}
\begin{align}
\nonumber
\underline{\epsilon}^{0}_{\omega}(\mathbf{r})=\left(
 \begin{matrix}
  \alpha_{\omega}^{0}(\mathbf{r}) & i\delta_{\omega}^{0}(\mathbf{r})\\
  -i\delta_{\omega}^{0}(\mathbf{r}) & \alpha_{\omega}^{0}(\mathbf{r})
 \end{matrix}
\right),\\
\label{eq:alpha_delta}
\alpha_{\omega}^{0}(\mathbf{r})=1-\frac{\omega_p^2(\mathbf{r})}{\omega^2-\omega_c^2(\mathbf{r})},\; \delta_{\omega}^{0}(\mathbf{r})=\frac{\omega_c(\mathbf{r})\omega_p^2(\mathbf{r})}{\omega(\omega^2-\omega_c^2(\mathbf{r}))}.
\end{align}

The point $\mathbf{r}_c=(x_c,y_c)$ s.t. $\omega_c(\mathbf{r}_c)=\omega$, i.e. when $\underline{\epsilon}_{\omega}^{0}(\mathbf{r})$ is singular, is called a cyclotron resonance (c.f. \cite[Chapter 1-5]{Stix}). 
In \cite{singular_solutions} it was demonstrated for a 1D-counterpart of the above system that such points behave like removable singularities, 
and the solutions are well-defined in the limit $x\rightarrow x_c$. Hence this case is not of interest for the present work.

Another interesting case is $\omega_p^2(\mathbf{r})+\omega_c^2(\mathbf{r})=\omega^2$, when the diagonal part of the tensor $\underline{\epsilon}_{\omega}^{0}(\mathbf{r})$ vanishes, 
under the condition that the non-diagonal part remains non-zero. This is a hybrid resonance case. 
As shown in \cite{Despres_2014, singular_solutions}, for a 1D-counterpart of (\ref{eq:model_freq_domain}), in this case the time-harmonic electric field component $E_x$ is not necessarily square 
integrable. This apparent paradox is of course the source of important numerical difficulties which are the subject of the present study.  
Jumping ahead, instead of (\ref{eq:model_freq_domain}) 
one considers a sequence of regularized problems
\begin{align}
\label{eq:seq_regularized}
  \mathbf{curl}{\operatorname{curl}}\hat{\mathbf{E}}-\frac{\omega^2}{c^2}\underline{\epsilon}^{\nu}_{\omega}(\mathbf{r})\hat{\mathbf{E}}=0,\;
  \underline{\epsilon}^{\nu}_{\omega}(\mathbf{r})= \underline{\epsilon}^{0}_{\omega}(\mathbf{r})+i\nu \mathbb{E},\; 
\end{align}
with $\nu\rightarrow 0$. 
}

\urev{We will concentrate on a simplified model (which nevertheless is of physical interest when modelling antennas in plasmas), where it is required to study the above system in an 
infinite domain $(-L,\; \infty)\times\mathbb{R}$, $L\in \mathbb{R}$, under the assumption that the electron density $N_{e}$ and the magnetic field $B_0$ are \textbf{uniform} in the second coordinate, more precisely 
$N_{e}=N_{e}(x)$ and $B_0=B_0(x)$, see e.g. \cite{Despres_2014}. Despite such a simplfication, already a 1D-version of the system (\ref{eq:main_model}) contains difficulties intrinsic to the hybrid resonance case
\cite{Despres_2014, singular_solutions}.

The problem (\ref{eq:model_freq_domain}) should be equipped with the boundary conditions.
At the left boundary of the domain, which represents the wall of the Tokamak, we choose Robin boundary conditions 
\be
-curl \hat{\mathbf{E}} -\imath \lambda\hat{\mathbf{E}} \wedge \n = g_{inc} = -curl \E_{inc} -\imath\lambda\E_{inc} \wedge \n,
\ee
where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$ and $\lambda$ is 
the frequency of the antenna. We truncate the domain 
$(-L,\; \infty)\times\mathbb{R}$ to $(-L,\; H)\times\mathbb{R}$ and set on the right boundary $\operatorname{curl} \E = 0$.

}

Hence, recalling that $N_e=N_e(x), \; B_0=B_0(x)$, we perform the Fourier transform in $y$ ($\partial_y\rightarrow i\theta, \; \theta\in\mathbb{R},$) and consider the one-dimensional setting

\begin{equation}
\label{eq:main_model}
\begin{cases}
\epsilon_0\partial_t E_{x}-i\theta H_z=-eN_e u_x,\\
\epsilon_0\partial_t E_{y}+\partial_x H_z=-eN_e u_y,\\
\mu_0\partial_t H_z+\partial_x E_y-i\theta E_x =0,\\
m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\\
m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y
\end{cases}
\end{equation}
 posed in $(-L,\; H)$, for some $L,H>0$, with the boundary conditions 
 \begin{align*}
  \left.\left(-\partial_x E_y+i\theta E_x -\imath \lambda E_y\right)\right|_{x=-L} =g_{inc},\\
  \left.\partial_xE_y\right|_{x=H}=0.
 \end{align*}
This is the model that will be considered in the rest of the article, unless stated otherwise.

@@

%\begin{remark}
%	When modelling antennas in plasma physics \mrev{(e.g. in such applications as ITER)}, 
%	a good choice of boundary condition could be $\lambda = \sqrt{\alpha_{\omega}(-L)}$
%\end{remark}

@@

Second, we briefly develop an original scheme based on widely appreciated semi-lagrangian schemes
for the discretization of time domain Maxwell's equations with a linear current.
Thirdly, we consider the case $\nu\rightarrow 0$, and study the limiting amplitude solution 
$\lim\limits_{t\rightarrow +\infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}(t)$ obtained with the help of 
the FDTD discretization of \eqref{eq:main_model}, suggested in \cite{stable_yee_plasma_current}. 
We compare this result with 
$\hat{\mathbf{E}}\mathrm{e}^{i\omega t}$, computed in the frequency domain, for $\nu\rightarrow 0$, which is equivalent to considering
$\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}\mathbf{E}(t)$.
\textcolor{red}{Such a comparison is a way to study the formal commutation relation between the limited absorption and the limiting amplitude principles. 
In application to e.g. non-resonant case of (\ref{eq:model_freq_domain}), the limited absorption principle states that with 
appropriately chosen boundary conditions the solution of (\ref{eq:seq_regularized}) 
as $\nu\rightarrow 0\pm$ 
would coincide with the solution of (\ref{eq:model_freq_domain}). Similarly, the limiting amplitude principle applied to the problem (\ref{eq:main_system}) 
states that if the boundary conditions are chosen harmonic in time, e.g. $\partial_x E_y=\mathrm{e}^{-i\omega_{*} t}$ on 
the boundary, then the solution of this problem $(\mathbf{E}(t),\;H(t))$ asymptotically ($t\rightarrow +\infty$)
tends to a steady state of the form $ \left(\mathbf{E}(\omega_{*}),\; \hat{H}(\omega_{*})\right)\mathrm{e}^{-i\omega_{*} t}$, where 
$\left(\hat{\mathbf{E}}(\omega_{*}),\; \hat{H}(\omega_{*})\right)$ is the solution of (\ref{eq:main_model})
in the frequency domain, with $\omega=\omega_{*}$. For more details see e.g. \cite{Morawetz, Eidus}. The commutation between the two principles then write as}
$$
\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}= \lim\limits_{t\rightarrow+\infty}\lim\limits_{\nu\rightarrow 0},
$$
see Figure \ref{fig:limits}. 
Even though it is true for standard linear wave problems, it is not clear \mrev{if it still holds} in our case due the singularity
of the hybrid resonance.
\begin{figure}
\begin{tikzpicture}
   \matrix (m) [matrix of math nodes,row sep=3em,column sep=4em,minimum width=2em] {
     \mathbf{E}^{\nu}(t) & \mathbf{E}^{0+}(t)\\
     \hat{\mathbf{E}}^{\nu}(t)\mathrm{e}^{i\omega t} & 
    \lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow \infty}\mathbf{E}^{\nu}(t)=\lim\limits_{t\rightarrow \infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}^{\nu}(t)\\
     };
 \path[-stealth,font=\scriptsize]    (m-1-1) edge node [left] {$t\rightarrow+\infty$} (m-2-1);
  \path[-stealth, font=\scriptsize]   (m-1-1) edge node [above] {$\nu\rightarrow 0+$} (m-1-2);
 \path[-stealth, font=\scriptsize]   (m-2-1) edge node [above] {$\nu\rightarrow 0$} (m-2-2);
  \path[-stealth, font=\scriptsize]   (m-1-2) edge node [right] {$t\rightarrow +\infty$} (m-2-2);
